GPU-friendly Stroke Expansion

### 2024-06-14 paper.tex
textasciitilde and fixes the bump memory table caption

We authored two additional test scenes in order stress the GPU with a higher workload. The first is a very large stroked path with ~500,000 individually styled dashed segments which we adapted from Skia's open-source test corpus. We used two variants of this scene with \emph{butt} and \emph{round} cap styles. For the second scene we adapted the \emph{Canvas Paths} test case from MotionMark~[\citenum{MotionMark}], which renders a large number of randomly generated stroked line, quadratic, and cubic Bézier paths. We made two versions with different sizes: mmark-70k and mmark-120k with 70,000 and 120,000 path segments, respectively. Table~\ref{table:bump-counts} shows the payload sizes of our largest test scenes.

@@

Figures~\ref{fig:nehab-gpu-timings} and \ref{fig:test-scenes-gpu-timings} show the execution times for the two data sets. The entire \citet{Nehab2020} timings set adds up to less than 1 ms on all GPUs except the mobile unit. Our algorithm is ~14$\times$ slower on the Mali-G78 compared to the M1 Max but it is still capable of processing \emph{waves} in 3~ms. We observed that the performance of the kernel scales well with increasing GPU ability even at very large workloads, as demonstrated by the order-of-magnitude difference in run time between the mobile, laptop, and high-end desktop form factors we tested. We also confirmed that outputting arcs instead of lines can lead to a 2$\times$ decrease in execution time (particularly in scenes with high curve content, like \emph{waves} and \emph{mmark}) as predicted by the lower overall primitive count.

@@

\begin{table}
    \caption{The estimated and actual \emph{line soup} buffer sizes for scenes rendered at 2088x1600 resolution. Our estimation uses Wang's formula combined with a scaling heuristic based on the linewidth. In the worst case, our buffer size estimator overshoots by a factor ~4.}
    \begin{tabular}{|l|c|c|}
    \hline
        \multicolumn{1}{|c|}{\textbf{Test}} & Actual Size & Estimated Size \\
    \hline
        roads.svg  & 2.76 MB   & 8.35 MB    \\
        waves.svg  & 10.89 MB  & 80.69 MB   \\
        mmark-70k  & 36.10 MB  & 103.06 MB  \\
        mmark-120k & 60.01 MB  & 177.33 MB  \\
    \hline
    \end{tabular}
    \label{table:bump-estimate-mem}
\end{table}

\begin{figure*}
    \centering
    \includegraphics[scale=0.2]{test_renderings}
    \caption{Renderings of some of our test scenes created using our algorithm. All images were rendered on an Apple M1 Max at 2088x1600 resolution using our GPU pipeline. \textbf{(a)} \emph{waves.svg} from the Nehab2020 timings data set (3.09~ms); \textbf{(b)} The \emph{mmark-120k} scene with 120,000 input segments (19.86~ms); \textbf{(c)} The \emph{long path} scene with ~500k input segments and round caps (25~ms including CPU-side dashing - the GPU time to render the scene is 9~ms); \textbf{(d)}; A simple test scene showcasing various cap and join styles (1.56~ms); \textbf{(e)} The famous \emph{Ghostscript Tiger} containing both stroked and filled paths (1.69~ms).}
    \Description{Renderings of the test scenes}
    \label{fig:renderings}
\end{figure*}

>>>>

We authored two additional test scenes in order stress the GPU with a higher workload. The first is a very large stroked path with \textasciitilde500,000 individually styled dashed segments which we adapted from Skia's open-source test corpus. We used two variants of this scene with \emph{butt} and \emph{round} cap styles. For the second scene we adapted the \emph{Canvas Paths} test case from MotionMark~[\citenum{MotionMark}], which renders a large number of randomly generated stroked line, quadratic, and cubic Bézier paths. We made two versions with different sizes: mmark-70k and mmark-120k with 70,000 and 120,000 path segments, respectively. Table~\ref{table:bump-counts} shows the payload sizes of our largest test scenes.

@@

Figures~\ref{fig:nehab-gpu-timings} and \ref{fig:test-scenes-gpu-timings} show the execution times for the two data sets. The entire \citet{Nehab2020} timings set adds up to less than 1 ms on all GPUs except the mobile unit. Our algorithm is \textasciitilde14$\times$ slower on the Mali-G78 compared to the M1 Max but it is still capable of processing \emph{waves} in 3~ms. We observed that the performance of the kernel scales well with increasing GPU ability even at very large workloads, as demonstrated by the order-of-magnitude difference in run time between the mobile, laptop, and high-end desktop form factors we tested. We also confirmed that outputting arcs instead of lines can lead to a 2$\times$ decrease in execution time (particularly in scenes with high curve content, like \emph{waves} and \emph{mmark}) as predicted by the lower overall primitive count.

@@

\begin{table}
    \caption{The estimated and actual \emph{line soup} buffer sizes for scenes rendered at 2088x1600 resolution. Our estimation uses Wang's formula combined with a scaling heuristic based on the linewidth. The estimate is conservative and always overshoots the actual memory requirement.}
    \begin{tabular}{|l|c|c|}
    \hline
        \multicolumn{1}{|c|}{\textbf{Test}} & Actual Size & Estimated Size \\
    \hline
        roads.svg  & 2.76 MB   & 8.35 MB    \\
        waves.svg  & 10.89 MB  & 80.69 MB   \\
        mmark-70k  & 36.10 MB  & 103.06 MB  \\
        mmark-120k & 60.01 MB  & 177.33 MB  \\
    \hline
    \end{tabular}
    \label{table:bump-estimate-mem}
\end{table}

\begin{figure*}
    \centering
    \includegraphics[scale=0.2]{test_renderings}
    \caption{Renderings of some of our test scenes created using our algorithm. All images were rendered on an Apple M1 Max at 2088x1600 resolution using our GPU pipeline. \textbf{(a)} \emph{waves.svg} from the Nehab2020 timings data set (3.09~ms); \textbf{(b)} The \emph{mmark-120k} scene with 120,000 input segments (19.86~ms); \textbf{(c)} The \emph{long path} scene with \textasciitilde500k input segments and round caps (25~ms including CPU-side dashing -- the GPU time to render the scene is 9~ms); \textbf{(d)}; A simple test scene showcasing various cap and join styles (1.56~ms); \textbf{(e)} The famous \emph{Ghostscript Tiger} containing both stroked and filled paths (1.69~ms).}
    \Description{Renderings of the test scenes}
    \label{fig:renderings}
\end{figure*}
